TGI-spinal-power

### 2022-05-16 analysis/tgispine_lme_power.Rmd
trying to create power calculation with glmmTMB but cannot find an aappropriate package. will simulate own tomorrow

# Now to model effects! Try a zero inflated regression model
```{r}
# First model cold VAS
model.cold = glmmTMB::glmmTMB(beta ~ manipulation + condition + cold_location + trial_n +
                                (1|ID),
                      family = glmmTMB::beta_family(),
                      ziformula = ~1+manipulation,
                      data = df_VAS[df_VAS$VAS == 'cold' ,],
                      na.action = na.omit)
# then model warm VAS
model.warm = glmmTMB::glmmTMB(beta ~ manipulation + condition + cold_location + trial_n +
                                (1|ID),
                      family = glmmTMB::beta_family(),
                      ziformula = ~1+manipulation,
                      data = df_VAS[df_VAS$VAS == 'warm' ,])
# model summaries
summary(model.cold)
summary(model.warm)
```
# Look at model assumptions
```{r}
# cold assumption
model.cold.assmup <- simulateResiduals(model.cold, n = 1000)
plot(model.cold.assmup)
```

@@

@@

# power analysis - using smallest effect size
fixef(model.cold.ex)[['cond']][['cold_locationprox_caud']] <- cold_loc_effect
pwr.cold <- powerSim(model.cold.ex)
print(pwr.cold)

>>>>

# Now to model effects! Try a zero inflated regression model
```{r}
# First model cold VAS
model.cold = glmmTMB::glmmTMB(beta ~ manipulation + condition + cold_location + trial_n +
                                (1|ID),
                      family = glmmTMB::beta_family(),
                      ziformula = ~1+manipulation,
                      data = df_VAS[df_VAS$VAS == 'cold' ,],
                      na.action = na.omit) 
# then model warm VAS
model.warm = glmmTMB::glmmTMB(beta ~ manipulation + condition + cold_location + trial_n +
                                (1|ID),
                      family = glmmTMB::beta_family(),
                      ziformula = ~1+manipulation,
# model summaries
summary(model.cold)
summary(model.warm)
```
# Look at model assumptions
```{r}
# cold assumption
model.cold.assmup <- simulateResiduals(model.cold, n = 1000)
plot(model.cold.assmup)
```

@@

# Extract coefficients (effect sizes) of interest from pilot data model
modelc.coefs <- model.cold.ex %>% summary() %>% 
  coef()

@@

# power analysis - using smallest effect size
(model.cold.ex)[['cond']][['cold_locationprox_caud']] <- cold_loc_effect
pwr.cold <- powerSim(model.cold.ex)
print(pwr.cold)

### 2022-05-16 analysis/tgispine_lmebeta_power.Rmd
trying to create power calculation with glmmTMB but cannot find an aappropriate package. will simulate own tomorrow

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lme4)
library(simr)
library(broom)
library(brms)
library(modelsummary)
library(tibble)
library(DHARMa)
library(glmmTMB)
library(reshape2)
library(tidyverse)
library(plyr)

@@

Cold model power analysis
# Run power analyses!!
# Cold first, then warm
# Create a model with more data points per variable, to extract more power

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lme4)
library(simr)
library(broom)
library(brms)
library(modelsummary)
library(tibble)
library(DHARMa)
library(glmmTMB)
library(reshape2)
library(tidyverse)
library(plyr)
library(betareg)

@@

# Run power analyses!!
This code is extracted from [TBD]
# Cold first, then warm

```{r}
# Extract coefficient sizes
modelc.coefs

GetHyperparam<-function(x,b=NULL){
  ## Get the hyperparameters from the mixed effect model
  fe <- fixef(x)

  if(is.null(b))
    b<-fe[2] # use the data effect size if not supplied
  mu.a <- fe[1] 
  vc <- VarCorr(x)
  sigma.y <- as.numeric(vc[5, 2]) # Residual StdDev
  sigma.a <- as.numeric(vc[2, 2]) # Cobblebar StdDev
  sigma.g <- as.numeric(vc[4, 2]) # Cobblebar:transect StdDev
  hp<-c(b, mu.a, sigma.y, sigma.a, sigma.g)
  names(hp)<-c("b", "mu.a", "sigma.y", "sigma.a", "sigma.g")
  return(hp)
}
```
